Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2021-11-12 write-up/fda-recurrent.tex
putting in plots
Updating paper
ADding plots  for appendix (to show heterogeneity)

\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage[stretch=10]{microtype}
%\usepackage{hyperref}
\def\struckint{\mathop{%
\def\mathpalette##1##2{\mathchoice{##1\displaystyle##2}%
 {##1\textstyle##2}{##1\scriptstyle##2}{##1\scriptscriptstyle##2}}%
\mathpalette
{\vbox\bgroup\baselineskip0pt\lineskiplimit-1000pt\lineskip-1000pt
\halign\bgroup\hfill$}
{##$\hfill\cr{\intop}\cr\diagup\cr\egroup\egroup}%
}\limits}
\usepackage{natbib}
\usepackage{color}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage{multirow}
\usepackage{floatrow}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]

@@

The focus here is on two physiological processes -- (1) electrodermal activity (EDA), a measure of skin conductance measured at 4Hz, and  (2) \emph{gACC}, a coordinate-free feature built from accelerometer data collected at 32Hz that measures physical movement.  Electrodermal activity can be significantly impacted by external factors (e.g., room temperature).  To account for the high between user-day variation, we analyze EDA standardized per study-day.
The individual EDA and gACC trajectories are highly variable which tends to obscure patterns and trends.  In Figure~\ref{fig:mean_edacc}, the mean trajectories of EDA and gACC are plotted in reverse time from button press timestamps and randomly sampled non-event timestamps. While there are certain similarities in the two plots, the differences in temporal trends are rather striking. In particular, we see sharp increases in EDA in the XX minutes prior to button presses, which is in marked contrast with levels in the six months prior to failure, as seen in the lower pair of curves.

\begin{figure}[!th]
\rule{3cm}{3cm}%
\caption{EDA and ACC plots for average at non-event and event times.}
\label{fig:mean_edacc}
\end{figure}

>>>>

\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage[stretch=10]{microtype}
%\usepackage{hyperref}
\def\struckint{\mathop{%
\def\mathpalette##1##2{\mathchoice{##1\displaystyle##2}%
 {##1\textstyle##2}{##1\scriptstyle##2}{##1\scriptscriptstyle##2}}%
\mathpalette
{\vbox\bgroup\baselineskip0pt\lineskiplimit-1000pt\lineskip-1000pt
\halign\bgroup\hfill$}
{##$\hfill\cr{\intop}\cr\diagup\cr\egroup\egroup}%
}\limits}
\usepackage{natbib}
\usepackage{color}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage{multirow}
\usepackage{floatrow}
\usepackage{subcaption}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]

@@

Here, we focus on two physiological processes -- (1) electrodermal activity (EDA), a measure of skin conductance measured at 4Hz, and  (2) \emph{gACC}, a coordinate-free feature built from accelerometer data collected at 32Hz that measures physical movement.  Electrodermal activity can be significantly impacted by external factors (e.g., room temperature).  To account for the high between user-day variation, we analyze EDA standardized per study-day and  device. The individual EDA and gACC trajectories are highly variable which tends to obscure patterns and trends.  In Figure~\ref{fig:mean_edacc}, the mean trajectories of EDA and gACC are plotted in reverse time from button press timestamps, which shows sharp changes in EDA and AI in the 10 minutes prior to button presses.

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_eda.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:mean_eda}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_ai.png}
  \caption{Activity Index (AI)
}  \label{fig:mean_acc}
\end{subfigure}
\caption{Average scaled EDA and AI in the 30 minutes prior to button presses}
\label{fig:mean_edacc}
\end{figure}
